\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{stackengine}
\stackMath
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Resource Access Protocols\\
{\footnotesize }
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Sheikh Muhammad Adib Bin Sh Abu Bakar}
\IEEEauthorblockA{\textit{Hochshule Hamm-Lippstadt} \\
\textit{B.Eng. Electronic Engineering}\\
Lippstadt, Germany \\
sheikh-muhammad-adib.bin-sh-abu-bakar@stud.hshl.de}

}

\maketitle
\input{abstract.tex}

\begin{IEEEkeywords}
real time system, resource, protocol 
\end{IEEEkeywords}

\input{introduction.tex}
%Real Time System
%predictibility

\input{task_scheduling.tex}
%task
%scheduling
%classification
%-preemtion
%-non-preemtion
%-dynamic
%-static
%-online
%periodic
%constraint
%-timming
%-resource
%schedubility test

\input{problem.tex}
%protocol invention


\input{rap.tex}
%Introduction
%Model Classification
%Terminology and Assumption

\section{Compare}

\section{Conclusion}

\section*{Acknowledgment}

I, Sheikh Muhammad Adib 

\begin{thebibliography}{00}

\bibitem{b1}"IEEE Standard for a Real-Time Operating System (RTOS) for Small-Scale Embedded Systems," in IEEE Std 2050-2018 , vol., no., pp.1-333, 24 Aug. 2018, doi: 10.1109/IEEESTD.2018.8445674.

\bibitem{b2} “Real-time systems overview and examples,” Intel. [Online]. Available: https://www.intel.com/content/www/us/en/robotics/real-time-systems.html. [Accessed: 04-May-2022]. 

\bibitem{b3}“Characteristics of real-time systems,” GeeksforGeeks, 04-May-2020. [Online]. Available: https://www.geeksforgeeks.org/characteristics-of-real-time-systems/. [Accessed: 04-Apr-2022]. 

\bibitem{b4} “Terminology and notation,” Terminology and Notation |. [Online]. Available: https://cmte.ieee.org/tcrts/education/terminology-and-notation/. [Accessed: 04-Apr-2022]. 

\bibitem{b5} G. C. Buttazzo, "Hard real-time computing systems: Predictable scheduling algorithms and applications". New York: Springer, 2011. 

\bibitem{b6} L. Sha, R. Rajkumar and J. P. Lehoczky, "Priority inheritance protocols: an approach to real-time synchronization," in IEEE Transactions on Computers, vol. 39, no. 9, pp. 1175-1185, Sept. 1990, doi: 10.1109/12.57058.

\bibitem{b7} Rajkumar, Raj and Juvva, Kanaka and Molano, Anastasio and Oikawa, Shuichi "Resource Kernels: A Resource-centric Approach to Real-Time and Multimedia Systems" 1997 Proceedings of SPIE - The International Society for Optical Engineering. 3310. 10.1117/12.298417. 

\bibitem{b8} Nakajima, Tatsuo and Tokuda, Hideyuki, "Real-Time Synchronization in Real-Time Mach", 1994 
\end{thebibliography}







\end{document}
